% !TEX encoding = UTF-8 Unicode
%!TEX root = thesis.tex
% !TEX spellcheck = en-US
%%=========================================

\chapter{Neuroevolution Application Dependencies}
\label{appendix:python_dependencies}

\begin{center}
\begin{longtable}{p{3.3cm} p{13cm}}
\caption[Dependencies]{Dependencies} \label{tab:neuroevolution_dependencies} \\

\hline \multicolumn{1}{l}{\textbf{Name}} & \multicolumn{1}{l}{\textbf{Description}} \\ \hline 
\endfirsthead

\multicolumn{2}{c}
{{\bfseries \tablename\ \thetable{} -- continued from previous page}} \\
\hline \multicolumn{1}{l}{\textbf{Name}} & \multicolumn{1}{l}{\textbf{Description}} \\ \hline 
\endhead

\hline \multicolumn{2}{r}{{Continued on next page}} \\ \hline
\endfoot

\hline \hline
\endlastfoot

\midrule
Jinja2 & A general purpose templating language. Useful for generating csd files that are fed into Csound. \\
\midrule
six, futures & Makes the Python application compatible with both Python 2 and Python 3 \\
\midrule
whichcraft & A tool that can check which programs are installed on the computer. Used for starting Node.js correctly on both Ubuntu and Windows. \\
\midrule
natsort & Natural sorting. Used for showing audio features in the correct order. \\
\midrule
nose & A tool for running all the automated tests in the project \\
\midrule
statistics & A package that can calculate various statistics, for example standard deviation, of data series. \\
\midrule
numpy & A package for scientific computing. Used for computing gradients and euclidean distance. \\
\midrule
matplotlib & A 2D plotting library. Used for creating various plots for this report. \\
\midrule
MultiNEAT & A portable neuroevolution Library written in C++. It has Python bindings. \\
\midrule
Sonic Annotator with Vamp plugin LibXtract & Sonic annotator takes in a set of audio files, runs them through the specified vamp plugin and outputs the results. LibXtract is a library for audio feature extraction. \\
\midrule
Aubio MFCC & A tool that takes in a single audio file and calculates and outputs MFCC coefficients for each frame \\
\midrule
Essentia music extractors & A tool that takes in a single audio file, calculates a large set of audio features and writes the resulting data to a file \\
\midrule
Csound & A sound and music computing system. Csound can be given a piece of Csound code that describes how to process audio, and then Csound processes the audio accordingly. In this project, Csound is used for A) applying audio effects with effect parameters that vary over time and B) calculating audio features. \\

\end{longtable}
\end{center}
