% !TEX encoding = UTF-8 Unicode
%!TEX root = thesis.tex
% !TEX spellcheck = en-US
%%=========================================
\chapter{Experiments and Discussion}
\label{chapter:experiments_and_discussion}

Five experiments have been conducted in an attempt to find good ways to use neuroevolution for finding useful mappings from audio features to audio effect parameters. In each experiment, different neuroevolution configurations are compared to find what works better. Due to the random nature of genetic algorithms, results vary from run to run. To deal with this, each configuration gets multiple runs (with different Pseudo Random Number Generator (PRNG) seeds), and results from the runs are aggregated and presented in various figures. Table \ref{tab:experiments_overview} shows a rough overview of the experiments.

\begin{center}
\begin{longtable}{p{2.3cm} p{13cm}}
\caption[Overview of experiments]{Overview of experiments} \label{tab:experiments_overview} \\

\hline \multicolumn{1}{l}{\textbf{Experiment}} & \multicolumn{1}{l}{\textbf{Description}} \\ \hline 
\endfirsthead

\multicolumn{2}{c}%
{{\bfseries \tablename\ \thetable{} -- continued from previous page}} \\
\hline \multicolumn{1}{l}{\textbf{Experiment}} & \multicolumn{1}{l}{\textbf{Description}} \\ \hline 
\endhead

\hline \multicolumn{2}{r}{{Continued on next page}} \\ \hline
\endfoot

\hline \hline
\endlastfoot

\midrule
  1 & Find a good combination of mutation rate and crossover rate \\
\midrule
  2 & Find a good value for structural mutation parameters \\
\midrule
  3 & Apply data augmentation to the target sound, and see if the result generalizes better \\
\midrule
  4 & Compare sets of audio features used in the fitness function. Analyze data from the neuroevolution process. \\
\midrule
  5 & Compare networks of audio effects with individual audio effects. \\
\end{longtable}
\end{center}

\section{General Configuration}
Table \ref{tab:general_configuration} shows the parameters used unless otherwise stated in individual experiments. The table is not exhaustive. A number of NEAT parameters were left at their respective default values\footnote{\url{https://github.com/peter-ch/MultiNEAT/blob/master/src/Parameters.cpp\#L42}}, set by \citeauthor{multineat}, the authors of MultiNEAT.

\begin{center}
\begin{longtable}{p{10cm} p{4cm}}
\caption[General experiment configuration]{General experiment configuration} \label{tab:general_configuration} \\

\hline \multicolumn{1}{l}{\textbf{Parameter}} & \multicolumn{1}{l}{\textbf{Value}} \\ \hline 
\endfirsthead

\multicolumn{2}{c}%
{{\bfseries \tablename\ \thetable{} -- continued from previous page}} \\
\hline \multicolumn{1}{l}{\textbf{Parameter}} & \multicolumn{1}{l}{\textbf{Value}} \\ \hline 
\endhead

\hline \multicolumn{2}{r}{{Continued on next page}} \\ \hline
\endfoot

\hline \hline
\endlastfoot

\midrule
  Population size & 20 \\
\midrule
  Add neuron probability & 0.01 \\
\midrule
  Remove neuron probability & 0.01 \\
\midrule
  Add link probability & 0.01 \\
\midrule
  Remove link probability & 0.01 \\
\midrule
  Elite fraction & 0.1 \\
\midrule
  Survival rate & 0.25 \\
\midrule
  Allow clones & Yes \\
\midrule
  Selection method & Tournament selection \\
\midrule
  Hidden activation function & Hyperbolic tangent \\
\midrule
  Output activation function & Sigmoid \\
\midrule
  Effect parameter low-pass filter cutoff frequency & 50 Hz \\
\midrule
  Fitness function & Local similarity \\
\end{longtable}
\end{center}

\input{experiment1}
\input{experiment2}
\input{experiment3}
\input{experiment4}
\input{experiment5}
